---
title: "tikzPres"
author: "William Murrah"
date: "09/14/2014"
output: 
    beamer_presentation:
       theme: "Madrid"
       colortheme: "default"
       includes:
         in_header: header.tex
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Binomial Model $\theta$

\begin{figure}
\centering
\begin{tikzpicture}
\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100, minimum size=10mm]

% 2. Nodes
%%%%%%%%%%
\node[box, fill=black!10] (K) {K};
\node[box, fill=black!10] (N) [right=of K] {N};
\node[main, fill=white!100, double] (theta) [above=of K] {$\theta$};
\node[main, fill=white!100] (ptheta) [above=of N] {$\theta \%$}; 
\node [anchor=east, text width=4cm] (dists) at (10, 1.5) {
          $K \sim Binomial(\theta, N)$\\
          $\theta = \theta \% / 100$ \\
          $\theta \% \sim Uniform(0, 100)$};
% 3. Arrows
%%%%%%%%%%%
\path (N)      edge [connect] (K)
      (theta)  edge [connect] (K)
      (ptheta) edge [connect] (theta);

\end{tikzpicture}
\end{figure}


## figure from file
\begin{center}
   \includegraphics{figure.pdf}
\end{center}
## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## Linear Regression

\begin{tikzpicture}[
    thick,
    >=stealth',
    dot/.style = {
      draw,
      fill = white,
      circle,
      inner sep = 0pt,
      minimum size = 4pt
    }
  ]
  \coordinate (O) at (0,0);
  \draw[->] (-0.3,0) -- (8,0) coordinate[label = {below:$x$}] (xmax);
  \draw[->] (0,-0.3) -- (0,5) coordinate[label = {right:$f(x)$}] (ymax);
  \path[name path=x] (0.3,0.5) -- (6.7,4.7);
  \path[name path=y] plot[smooth] coordinates {(-0.3,2) (2,1.5) (4,2.8) (6,5)};
  \scope[name intersections = {of = x and y, name = i}]
    \fill[gray!20] (i-1) -- (i-2 |- i-1) -- (i-2) -- cycle;
    \draw      (0.3,0.5) -- (6.7,4.7) node[pos=0.8, below right] {Sekante};
    \draw[red] plot[smooth] coordinates {(-0.3,2) (2,1.5) (4,2.8) (6,5)};
    \draw (i-1) node[dot, label = {above:$P$}] (i-1) {} -- node[left]
      {$f(x_0)$} (i-1 |- O) node[dot, label = {below:$x_0$}] {};
    \path (i-2) node[dot, label = {above:$Q$}] (i-2) {} -- (i-2 |- i-1)
      node[dot] (i-12) {};
    \draw           (i-12) -- (i-12 |- O) node[dot,
                              label = {below:$x_0 + \varepsilon$}] {};
    \draw[blue, <->] (i-2) -- node[right] {$f(x_0 + \varepsilon) - f(x_0)$}
                              (i-12);
    \draw[blue, <->] (i-1) -- node[below] {$\varepsilon$} (i-12);
    \path       (i-1 |- O) -- node[below] {$\varepsilon$} (i-2 |- O);
    \draw[gray]      (i-2) -- (i-2 -| xmax);
    \draw[gray, <->] ([xshift = -0.5cm]i-2 -| xmax) -- node[fill = white]
      {$f(x_0 + \varepsilon)$}  ([xshift = -0.5cm]xmax);
  \endscope
\end{tikzpicture}