---
title: "Principles of Bayesian Statistics"
author: "William Murrah"
date: "10/17/2014"
output: 
   pdf_document:
      includes:
         in_header: header.tex
---

```{r opts}
library(knitr)
opts_knit$set(root.dir='../../')
getwd()
```

## Bayes Theorem:

$$
p(B | A) = \frac{p(A|B)p(A)}{p(A)}.
$$

**proof:**

We know that $p(A,B) = p(A|B)p(B)$ and $p(B,A) = p(B|A)p(A)$. We also know that $p(A,B) = p(B,A)$. Therefore we know:

$$
p(B|A)p(A) = p(A|B)p(B).
$$

If we divide both sides of this equation by $p(A)$, we get Bayes Theorem.


# Polling Example

This example is taken from Chapters 1 and 2 of *Introduction to Applied Bayesian Statistics adn Estimation for Social Scientists* by Scott Lynch.

```{r}
K <- seq(0,1, .01)

posterior <- qbeta(K, 1498, 1519)
prior <- qbeta(K, 942, 1008)
likelihood <- qbeta(K, 557, 512)
plot(density(posterior), xlim=c(.4,.6),
     main='Prior, Posterior, and Likelihood Densities for Polling Example',
     ylab='f(K)', xlab='K')
abline(v=.5, lty=17)
lines(density(prior), col='blue', lty=15 )
lines(density(likelihood), col='red', lty=20)
text(.56, 15, "Likelihood", col='red')
text(.52, 35, "Posterior", col='black')
text(.46, 22, "Prior", col='blue')
```

\centering
\begin{tikzpicture}
\tikzstyle{main}=[circle, minimum size = 10mm, thick, draw =black!80, node distance = 16mm]
\tikzstyle{connect}=[-latex, thick]
\tikzstyle{box}=[rectangle, draw=black!100, minimum size=10mm]

% 2. Nodes
%%%%%%%%%%
\node[box, fill=black!10] (K) {K};
\node[box, fill=black!10] (N) [right=of K] {N};
\node[main, fill=white!100, double] (theta) [above=of K] {$\theta$};
\node[main, fill=white!100] (ptheta) [above=of N] {$\theta \%$}; 
\node [anchor=east, text width=4cm] (dists) at (10, 1.5) {
          $K \sim Binomial(\theta, N)$\\
          $\theta = \theta \% / 100$ \\
          $\theta \% \sim Uniform(0, 100)$};
% 3. Arrows
%%%%%%%%%%%
\path (N)      edge [connect] (K)
      (theta)  edge [connect] (K)
      (ptheta) edge [connect] (theta);

\end{tikzpicture}
