---
title: "Title"
author: "William Murrah"
date: "10/06/2014"
output: pdf_document
---

```{r opts}
library(knitr)

```


```{r}
library(psych)
library(xtable)
options(xtable.comment = FALSE)
x = -1000:1000
y = function(x) 1/x
plot(x,y(x), type='l')

```
$$\lim_{x \to \infty}, \frac{1} {x}$$

```{r}
x = 1000:-1000
y = function(x) 1/x
plot(x,y(x), type='l')
```

```{r}
x = -1000:1000
y = function (x) (x^2 + 5)/3
plot(x, y(x), type='l')

```

```{r}
x = 1000:-1000
y = function (x) (x^2 - 1)/5
plot(x, y(x), type='l')

```


```{r}
x = -1000:1000
y = function (x) exp(-x)
plot(x, y(x), type='l')

```

```{r}
x = 1000:-1000
y = function (x) exp(-x)
plot(x, y(x), type='l')

```

```{r}
x = -1000:1000
y = function (x) x/2*x
plot(x, y(x), type='l')

```

```{r}
x = -1000:1000
mu = 0
sigma = 1:2001
y = function (x) 1/(sigma*sqrt(2*pi)*(-(x - 0)^2)/(2*sigma^2))
plot(x, y(x), type='l')

```



## Matix Algebra

```{r}

A = matrix(c(3,-1,2,3), nrow=2)
A
B = matrix(c(3,4,10,1,3,4,-1,5,1), nrow=3)
B
C = matrix(c(1,7,4),nrow=1)
C
D = matrix(c(2,9,3), nrow=3)
D
E = matrix(c(4,7,6, 1,1,8, 3,8,7), nrow=3)
E
```

```{r, results='asis'}
BE <- B + E
print(xtable(BE, digits=0, caption="$B + E$"))
```

```{r}
E - B
```

```{r}
# A%*%B non-conformable 
```
```{r}
C %*% D
```
```{r}
D %*% C
```

```{r}
# D %*% E non-conformable
```

```{r}
t(E)
```

```{r}
det(A)
```

```{r}
det(B)
```

```{r}
solve(E)
```

```{r}
tr(B)
```


## Chapter 2

1.

2. Probability of finding 3 heads in a row:

```{r}

.5 * .5 * .5
```

3. Probability of finding 3 heads in a row with bend coin (p = .7)
```{r}
.7 * .7 * .7

# or 

.7^3
```

4. 3 heads or 3 tails in a row
```{r}
.5^3 + .5^3

```

5. 3 heads and one tail (order irrelevant):

$$ {n \choose k} p^k(1-p^{n-k})$$

```{r}
choose(4,3)*(.5^3 * .5^1)
```

6. normal approximation of binomial:

$$ \mu_x = np, \quad \sigma_x = \sqrt{np(1 - p)}$$

```{r}

mu = 200*.5
sigma.x = sqrt(200*.5*(1 - .5))
z = (130 - mu)/ sigma.x
```


7. Plot a normal distribution with parameters $\mu = 5$ and $\sigma = 2$.
```{r}
plot(seq(0, 10, by=.1), dnorm(seq(0, 10, by=.1), 5,2), type='l')
```

8. Plot a normal distribution with parameters $\mu = 2$ and $\sigma = 5$.

```{r}
plot(seq(-6,10, by=.1), dnorm(seq(-6,10,by=.1), 2,5), type='l')
```

8. Plot a normal distribution with parameters $\mu = 2$ and $\sigma = 5$.
9. Plot the t(0, 1, df = 1) and t(0, 1, df = 10) distributions. Note: $\Gamma$ is a
function. The function is: $\Gamma (n) = e^{-u} u^{n-1}du$. For integers, 
$\Gamma (n) = 0(n - 1)$ Thus, $\Gamma (4) = (4 - 1)! = 6$. However, when the argument to the
function is not an integer, this formula will not work. Instead, it is easier
to use a software package to compute the function value for you.


```{r}

```



